The {TestIdeals} package for \emph{Macaulay2}

### 2019-04-29 Fsing/TestIdealsPaper/TestIdeals.tex
Finsehd recomputing examples.

\medskip
{\small
\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];

@@

\medskip
{\small
   \setstretch{.7}
\begin{MyVerbatim}
i1 : S = ZZ/5[x,y,z];

@@

\medskip
{\small
   \setstretch{.7}
\begin{MyVerbatim}
i1 : p = 3;

@@

\medskip
{\small
   \setstretch{.7}
\begin{MyVerbatim}
i8 : S = ZZ/3[a..f,x,y];

@@

\medskip
{\small
   \setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/2[a,b,c,d];

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i7 : U = matrix entries E2;

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i10 : V = ascendModule(1, A, U)

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^5 + (y + 1)^5 + z^5);

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y];

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^3 + (y + 1)^3 + z^3);

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : S = ZZ/3[a,b,c,d,t];

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^4 + y^4 + z^4);

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(y*z, x*z, x*y);

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/2[a..e];

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : T = ZZ/7[x,y];

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i7 : toString QGorensteinGenerator(1, R)

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : T = ZZ/3[x,y];
i2 : S = ZZ/3[a,b,c,d];
i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
i4 : I = ker f;
i5 : R = S/I;
i6 : testIdeal R
o6 = ideal 1
o6 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
i2 : L = FPureModule R;
i3 : L#0
                          2        2   3
o3 = ideal (0, y*z, x*z, y , x*y, x , z )
o3 : Ideal of R
i4 : L#1
o4 = ideal 1
o4 : Ideal of R
i5 : L#3
o5 = 1
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[x,y,z];
i2 : f = x^3 + y^2*z + y*z^2;
i3 : frobeniusPower(1/2, ideal f)
o3 = ideal (x, y, z)
o3 : Ideal of R
i4 : u=f^3;
i5 : frobeniusPower(1/4, ideal u)
o6 = ideal (x, y, z)
o6 : Ideal of R
i7 : ((FPureModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3 - x^5 - 2*z^5;
i3 : frobeniusPower(1/11, ideal f^10)
             2        3
o6 = ideal (z , x*z, x )
o3 : Ideal of R
i5 : frobeniusPower(1/121, ideal f^120)
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((FPureModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/3[u,v];
i2 : u = u^2*v^2;
i3 : compatibleIdeals u
o3 = {ideal v, ideal (v, u), ideal u}
o3 : List
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[a..f];
i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
             2       4
o2 : Matrix R  <--- R
i3 : I = minors(2, E);
o3 : Ideal of R
i4 : S = R/I;
i5 : isCohenMacaulay S
o5 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i6 : omega = canonicalIdeal S
o6 = ideal (e, d, a)
o6 : Ideal of S
i7 : omega = substitute(omega, R) + I;
o7 : Ideal of R
i8 : u = intersect((frobenius I):I, (frobenius omega) : omega);
o8 : Ideal of R
i9 : u = compress((gens u) % gens(frobenius I))
o9 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
             1       1
o9 : Matrix R  <--- R
i10 : u = first first entries u
       3       3       2                         2     2 2       2 2    3 2
o10 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e
o10 : R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i11 : L = compatibleIdeals u;
i12 : print \ L;
        3       3       2                         2     2 2       2 2    3 2
ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
               2
ideal (a + b, a  + d*e)
ideal (d, a)
ideal (d, a, e)
ideal (e, d, a, c)
ideal (e, d, c, b, a)
ideal (e, d, b, a)
ideal (d, a, c)
ideal (d, c, b, a)
ideal (d, b, a)
                      2
ideal (c + d, a + b, b  + d*e)
ideal (c + d, b, a, e)
ideal (b, a, e)
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i13 : print \ unique apply(L, J -> J : omega);
        3       3       2                         2     2 2       2 2    3 2
ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
               2
ideal (a + b, b  + d*e)
ideal (d, a)
ideal (e, d, a)
ideal 1
ideal (d, c, a)
ideal (d, c, b, a)
ideal (d, b, a)
                      2
ideal (c + d, a + b, b  + d*e)
ideal (e, c + d, b, a)
ideal (e, b, a)
\end{MyVerbatim}
}
\medskip

>>>>

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];

@@

\medskip
{\small
   \setstretch{.67}
\begin{MyVerbatim}
i1 : S = ZZ/5[x,y,z];

@@

\medskip
{\small
   \setstretch{.67}
\begin{MyVerbatim}
i1 : p = 3;

@@

\medskip
{\small
   \setstretch{.67}
\begin{MyVerbatim}
i8 : S = ZZ/3[a..f,x,y];

@@

\medskip
{\small
   \setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/2[a,b,c,d];

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i7 : U = matrix entries E2;

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i10 : V = ascendModule(1, A, U)

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^5 + (y + 1)^5 + z^5);

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y];

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^3 + (y + 1)^3 + z^3);

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : S = ZZ/3[a,b,c,d,t];

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^4 + y^4 + z^4);

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(y*z, x*z, x*y);

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/2[a..e];

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i1 : T = ZZ/7[x,y];

@@

\medskip
{\small\setstretch{.67}
\begin{MyVerbatim}
i7 : toString QGorensteinGenerator(1, R)

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i2 : T = ZZ/3[x,y];

i3 : S = ZZ/3[a,b,c,d];

i4 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});

o4 : RingMap T <--- S

i5 : I = ker f;

i6 : R = S/I;

i7 : testIdeal R

o7 = ideal 1

o7 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i2 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );

i3 : L = FPureModule R;

i4 : L#0

                       2        2   3
o4 = ideal (y*z, x*z, y , x*y, x , z )

o4 : Ideal of R

i5 : L#1

o5 = ideal 1

o5 : Ideal of R

i6 : L#3

o6 = 1i2 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );

i3 : L = FPureModule R;

i4 : L#0

                       2        2   3
o4 = ideal (y*z, x*z, y , x*y, x , z )

o4 : Ideal of R

i5 : L#1

o5 = ideal 1

o5 : Ideal of R

i6 : L#3

o6 = 1
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i2 : R = ZZ/2[x,y,z];

i3 : f = x^3 + y^2*z + y*z^2;

i4 : frobeniusPower(1/2, ideal f)

o4 : Ideal of R

i5 : u=f^3;

i6 : frobeniusPower(1/4, ideal u)

o6 = ideal (z, y, x)

i7 : ((FPureModule(1, f))#3) + 1

o7 = 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i2 : R = ZZ/11[x,y,z];

i3 : f = y^2*z^3 - x^5 - 2*z^5;

i4 : frobeniusPower(1/11, ideal f^10)

             2        3
o4 = ideal (z , x*z, x )

o4 : Ideal of R

i5 : frobeniusPower(1/121, ideal f^120)

             2        3
o5 = ideal (z , x*z, x )

o5 : Ideal of R

i6 : ((FPureModule(1, f))#3) + 1

o6 = 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i2 : R = ZZ/3[u,v];

i3 : u = u^2*v^2;

i4 : compatibleIdeals u

o4 = {ideal v, ideal (v, u), ideal u}

o4 : List
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i2 : R = ZZ/2[a..f];

i3 : E = matrix {{a, b, b, e}, {d, d, c, a}};

             2       4
o3 : Matrix R  <--- R

i4 : I = minors(2, E);

o4 : Ideal of R

i5 : S = R/I;

i6 : isCohenMacaulay S

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i7 : omega = canonicalIdeal S

o7 = ideal (e, d, a)

o7 : Ideal of S

i8 : omega = substitute(omega, R) + I;

o8 : Ideal of R

i9 : u = intersect((frobenius I):I, (frobenius omega) : omega);

o9 : Ideal of R

i10 : u = compress((gens u) % gens(frobenius I))

o10 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |

              1       1
o10 : Matrix R  <--- R

i11 :  u = first first entries u

       3       3       2                         2     2 2       2 2    3 2
o11 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e

o11 : R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
L = compatibleIdeals u;

i13 : print \ L;
       3       3       2                         2     2 2       2 2    3 2
ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
               2
ideal (a + b, a  + d*e)
ideal (e, a, d)
ideal (e, d, a, c)
ideal (e, d, c, b, a)
ideal (e, d, b, a)
ideal (e, b, a)
ideal (e, b, a, c + d)
                      2
ideal (c + d, a + b, b  + d*e)
ideal (d, a)
ideal (d, a, c)
ideal (d, c, b, a)
ideal (d, b, a)
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
 print \ unique apply(L, J -> J : omega);
       3       3       2                         2     2 2       2 2    3 2
ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
               2
ideal (a + b, b  + d*e)
ideal (e, d, a)
ideal 1
ideal (e, b, a)
ideal (e, c + d, b, a)
                      2
ideal (c + d, a + b, b  + d*e)
ideal (d, a)
ideal (d, c, a)
ideal (d, c, b, a)
ideal (d, b, a)
\end{MyVerbatim}
}
\medskip
